\documentclass[11pt]{article}
\usepackage[a4paper,margin=0.75in]{geometry}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{multicol}
\definecolor{myblue}{RGB}{27,133,184}
\colorlet{bodytext}{black!80}  % or black!85 for slightly darker
\linespread{1.1}
\usepackage{fontspec}
\setmainfont{TeX Gyre Heros} % beautiful, full character set
\setsansfont{TeX Gyre Heros}   % matches well
% \setmonofont{Fira Code}        % modern monospace

\titleformat{\section}
  [block]
  {\Large\sffamily}{}{0pt}{\color{black}}[\color{myblue}\vspace{0.3ex}\hrule height 3pt width 1\textwidth]

% === Reusable Experience Block Header ===
\newcommand{\roleheader}[3]{%
  {\large\sffamily\textbf{#1} @ #2} \hfill \textit{#3}\\[-0.3em]
  \color{myblue}\rule{\linewidth}{1pt}\\[0.5em]\color{bodytext}
}

% === Experience Bullets Environment ===
\newenvironment{experiencebullets}{%
  \begin{itemize}[leftmargin=1.25em, itemsep=-0.25em]
    \renewcommand{\labelitemi}{\textbullet}
}{%
  \end{itemize}
}

\newenvironment{experience}[4]{%
  \roleheader{#1}{#2}{#3}%
  #4\vspace{0.5em}%
}{%
  \vspace{1em}
}


% === Experience Bullet Point with Action → Impact ===
\newcommand{\expbullet}[3]{%
  \item \textbf{[#1]} {#2} \textrightarrow{} \textit{#3}%
}

\newcommand{\aexpbullet}[2]{%
  \item {#1} \textrightarrow{} \textit{#2}%
}

% === Sub‑section heading inside an experience ===
\newcommand{\expsubsection}[1]{%
  \vspace{0.75em}%
  {\sffamily\bfseries #1}\\[-0.2em]
  \rule{0.15\linewidth}{1pt}\\[0.3em]
}

\newenvironment{impactsection}[2]{%
  \vspace{0.5em}%
  \textbf{[#1]}\\#2%
  \begin{itemize}[leftmargin=2em, itemsep=-1em]
}{%
  \end{itemize}
}

\newlist{arrowitem}{itemize}{1}
\setlist[arrowitem]{label=\textrightarrow{}, leftmargin=2em, noitemsep, topsep=0pt}

\newcommand{\expmultibullet}[3]{%
  \item \textbf{[#1]} #2
  \begin{arrowitem}
    #3
  \end{arrowitem}
}

\newcommand{\name}[1]{\noindent{\LARGE\sffamily\textbf{#1}}}
\newcommand{\contact}[1]{\begin{flushright} \small #1 \end{flushright}}
\usepackage[none]{hyphenat}
\raggedright


%\renewcommand{\textbf}[1]{\textcolor{black!95}{#1}}



\begin{document}
\pagestyle{empty}
\color{bodytext}

\name{Srinath H S}\\[0.5em]
\textbf{Principal Architect @ Bankbazaar.com}\\[0.3em]
srinath.hs@gmail.com \quad | \quad +91 95387 88470 \quad | \quad linkedin.com/in/srinathhs

17+ years of experience, leading and managing engineering teams to build secure, scalable platforms across startups and enterprises. Proven leader in driving cloud-native architecture, DevSecOps, observability, and automation. Adept at aligning platform strategy with business goals through cross-functional collaboration and hands-on execution.

\section*{Core Competencies}
\begin{itemize}[leftmargin=*, itemsep=-0.5em]
  \item \textbf{Leadership \& Technical Strategy:} Management of team size of 6, informal mentorship of 15+, hiring, talent development, Defining technical vision, creating success metrics and agile execution.
  \item \textbf{Project Planning \& Execution:} Driving initiatives from conception to delivery, cross-functional collaboration.
  \item \textbf{Cloud Architecture \& DevOps:} AWS, Kubernetes, Terraform, ansible, microservices.
  \item \textbf{DevSecOps \& Automation:} Vulnerability management, ISO / PCI compliance, automated incident response.
  \item \textbf{FinOps \& Cost Optimization:} Cloud cost reduction, resource efficiency, financial accountability.
  \item \textbf{Programming Languages:} Java (10+ years), Python (6+ years).
\end{itemize}

\section*{Experience}

\begin{experience}{Principal Architect}{Bankbazaar.com}{2019-Present, Bangalore}{%
    Leading the \textbf{AWS Cloud and DevOps} function and driving platform evolution across security, cost optimization, scalability, and developer experience.%
  }

  \begin{experiencebullets}

    \item \textbf{[Engineering management]} Cultivated a high-performing engineering culture with team of 6 engineers and broader mentoring 15 engineers
    {
      % \aexpbullet {Led hiring, performance feedback, and career progression}
      % {Fostered a collaborative environment that accelerated skill development and empowered engineers to make independent decisions}
    }

    \expbullet{DevOps \& Automation}{Defined microservice standards, standardized observability, and adopted Terraform for IaC}{Reduced service onboarding from days to <1 hour, cut P1 resolution times to <1 hour, and empowered team to operate production systems confidently.}

    \expbullet {AI Initiatives}{Championed and led AI adoption across the organization}
    {Evaluated and drove adoption of coding copilots (Cline.bot) and initiated projects for agentic BI and customer service auditing using Whisper and Bedrock.}

    \expbullet{Developer-First Security}{Integrated automated vulnerability detection and self-service traffic management}{Maintained >90\% compliance with 0 critical CVEs in production, ensuring security without compromising developer productivity.}

    \expbullet{FinOps \& Cost Optimization}{Led cloud optimization initiatives and established cost visibility across 20+ AWS accounts}{Reduced monthly AWS costs by \$50k, improved EKS cluster efficiency by 20\%, and implemented robust cost tracking and accountability.}

    \expbullet {COVID Response}{Led secure remote access implementation for 1000+ employees}
    {Ensured business continuity with zero security lapses using Akamai Zero Trust and HashiCorp Vault.}

    \expbullet {Data Center to AWS Migration}{Designed and drove the cloud migration strategy for core services}
    {Improved uptime to >99.9\%, cut disaster recovery time to <1 hour, and reduced latency by 50\%, boosting SEO ranking.}
  \end{experiencebullets}

\end{experience}

\begin{experience}{Principal Software Engineer}{Digilend.in}{2017-2019, Bangalore}
  {\textbf{[FinTech lending platform]} Part of the \textbf{early startup team},
    working directly with the founders. Delivered features across the stack and also maintaining the \textbf{AWS Cloud (EC2, RDS)}
  }
  \begin{experiencebullets}
    \expbullet {Behavior model}{Built real-time user behavior tracking and dynamic journeys based on behavior}{Improved user loan approval rates by 15\%.}
    \expbullet {Website Performance}{Refactored and reduced AngularJS bundle size for key customer flows}{Reduce page load time to under 15(sec) and improved experience for customers with unreliable internet}
    \expbullet {Business Operations Automation}{Automated filling of loan application forms to reduce errors and improve on-ground agent performance.}{Document collection time reduced to less than 15 minutes per customer.}
  \end{experiencebullets}
\end{experience}


\begin{experience}{Software Specialist}{Hewlett Packard Enterprise}{2011-2017, Bangalore}{Worked on enterprise tape storage management tool, focusing on UI modernization, API design, and cross-release feature development.}
  % \begin{experiencebullets}
  %   \item \textbf{[UI Modernization]} Designed new UI according to HPE UI guidelines and Lead the team of 4 engineers to implement them as a transition from Flash to HTML5/React.js.
  %   \item \textbf{[Rest API design]} Defined and delivered RESTful APIs for new React UI.
  % \end{experiencebullets}
\end{experience}

\begin{experience}{Software Engineer}{IBM India Software Labs}{2008-2011, Bangalore}{Full-stack engineer and lab systems administrator working on management tool for IBM Power Systems.}
  % \begin{experiencebullets}
  %   \item \textbf{[Full-Stack Development]} Delivered UI/backend features, bug fixes across multiple releases of the Power Management Console.
  %   \item \textbf{[Data center management]} Planned, Implemented and Maintained lab test environments for continuous development using DS5000, N3600, VMware ESXi and IBM power servers.
  % \end{experiencebullets}
\end{experience}

\section*{Awards \& Recognition}
\begin{itemize}[leftmargin=*, itemsep=0em]
  \item First place in Circuit Design during Eccentric 2006, Dept. of E\&C, MSRIT, Bangalore.
  \item Top 10 team in “Mission to Mars”, Shasthra 2007, IIT Madras.
\end{itemize}


\section*{Education, Certifications \& Online Learning}

\textbf{Bachelor of Engineering in Electronics \& Communication} \\
Sapthagiri College of Engineering (VTU), Bangalore \hfill \textit{Aggregate: 75.90\%} \textit{2004–2008}  \\

\vspace{0.5em}
\textbf{Cryptography - I, Prof. Dan Boneh, Stanford University - Coursera} \hfill \textit{Sep 2013} \\

\textbf{Machine Learning, Prof. Andrew Ng, Stanford University - Coursera} \hfill \textit{Dec 2011} \\

\end{document}
