\documentclass[11pt]{article}
\usepackage[a4paper,margin=0.75in]{geometry}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{longtable} 
\definecolor{myblue}{RGB}{27,133,184}
\colorlet{bodytext}{black!80}  % or black!85 for slightly darker
\linespread{1.1}
\usepackage{fontspec}
\setmainfont{TeX Gyre Pagella} % beautiful, full character set
\setsansfont{TeX Gyre Heros}   % matches well
% \setmonofont{Fira Code}        % modern monospace

\titleformat{\section}
  [block]
  {\Large\sffamily}{}{0pt}{\color{black}}[\color{myblue}\vspace{0.3ex}\hrule height 3pt width 1\textwidth]

% === Reusable Experience Block Header ===
\newcommand{\roleheader}[3]{%
  {\large\sffamily\textbf{#1} @ #2} \hfill \textit{#3}\\[-0.3em]
  \color{myblue}\rule{\linewidth}{1pt}\\[0.5em]\color{bodytext}
}

% === Experience Bullets Environment ===
\newenvironment{experiencebullets}{%
  \begin{itemize}[leftmargin=1.25em, itemsep=-0.25em]
    \renewcommand{\labelitemi}{\textbullet}
}{%
  \end{itemize}
}

\newenvironment{experience}[4]{%
  \roleheader{#1}{#2}{#3}%
  #4\vspace{0.5em}%
}{%
  \vspace{1em}
}


% === Experience Bullet Point with Action → Impact ===
\newcommand{\expbullet}[3]{%
  \item \textbf{[#1]} {#2} \textrightarrow{} \textit{#3}%
}

\newcommand{\aexpbullet}[2]{%
  \item {#1} \textrightarrow{} \textit{#2}%
}

% === Sub‑section heading inside an experience ===
\newcommand{\expsubsection}[1]{%
  \vspace{0.75em}%
  {\sffamily\bfseries #1}\\[-0.2em]
  \rule{0.15\linewidth}{1pt}\\[0.3em]
}

\newenvironment{impactsection}[2]{%
  \vspace{0.5em}%
  \textbf{[#1]}\\#2%
  \begin{itemize}[leftmargin=2em, itemsep=-1em]
}{%
  \end{itemize}
}

\newlist{arrowitem}{itemize}{1}
\setlist[arrowitem]{label=\textrightarrow{}, leftmargin=2em, noitemsep, topsep=0pt}

\newcommand{\expmultibullet}[3]{%
  \item \textbf{[#1]} #2
  \begin{arrowitem}
    #3
  \end{arrowitem}
}

\newcommand{\name}[1]{\noindent{\LARGE\sffamily\textbf{#1}}}
\newcommand{\contact}[1]{\begin{flushright} \small #1 \end{flushright}}
\usepackage[none]{hyphenat}
\raggedright


%\renewcommand{\textbf}[1]{\textcolor{black!95}{#1}}



\begin{document}
\pagestyle{empty}
\color{bodytext}

\name{Srinath H S}\\[0.5em]
\textbf{Principal Architect @ Bankbazaar.com}\\[0.3em]
srinath.hs@gmail.com \quad | \quad +91 95387 88470 \quad | \quad linkedin.com/in/srinathhs

17+ years of experience building secure, scalable platforms across startups and enterprises.
Lead the DevOps function to drive cloud-native architecture, DevSecOps, observability, and automation.
Known for aligning platform strategy with business goals through cross-functional collaboration and hands-on execution.


\section*{Experience}

\begin{experience}{Principal Architect}{Bankbazaar.com}{2019-Present, Bangalore}{%
    Built and manage the platform serving \textbf{1M+ daily active users}. Leading the \textbf{AWS Cloud and DevOps} function and driving platform evolution across security, cost optimization, scalability, and developer experience.%
  }

  \begin{experiencebullets}
    
    \expmultibullet {Development}{Architected and Led the development of complex financial systems}
    {
        \aexpbullet{Contributed to over 100+ microservices built with Spring Boot, Kafka, MariaDB, and Cassandra, featuring a complex architecture with ReactJS and NodeJS}{Enhanced system functionality and reliability across the platform}
        \aexpbullet{Designed and led the implementation of several new, critical microservices from the ground up}{Delivered key business features and improved system modularity}
        \aexpbullet{Defined microservice architecture standards and deployment patterns}{Reduced new service onboarding time from 2 days to under 1 hour}
    }

    \expmultibullet {DevOps}{Built Scalable Infrastructure, Observability, and Incident Automation}
    {
      \aexpbullet {Standardized observability across all services by enforcing logging, alerting and metrics contracts}
      {Elimination of alerting gaps across the entire platform}
      
      \aexpbullet {Defined the incident response process for AWS and Kubernetes and guided the team to build and maintain standard runbooks}
      {Reduction P1 resolution times to < 1hour }
      
      \aexpbullet{Initiated and led automation of common alert response workflows; mentored team to build solutions independently}
      {Reduced incident response times to under 5 minutes for frequent issues}

      \aexpbullet{Spearheaded the definition and standardization of all AWS resources using Terraform}
      {Enabled consistent, scalable infrastructure as code across production environments}
      
      \aexpbullet{Organized and led hands-on knowledge-sharing sessions on Terraform, Kubernetes, and AWS Cloud}
      {Empowered the team to confidently debug, operate, and maintain production systems}
    }

    \expmultibullet {AI Initiatives}{Proposed and led AI Adoption across the organization.}
    {
      \item {Evaluated coding copilot options, benchmarked and drove the adoption of Cline.bot}
      \item {[InProgress] Driving in-house auditing of customer service agent interactions using Whisper and Bedrock.}
      \item {[InProgress] Identified and driving agentic solutions for business team to ask dynamic questions on BI data}
    }

    \expmultibullet {Security}{Proposed and led Scalable Developer-First Security Automation}
    {
      \aexpbullet {Implemented automated Fine-grained traffic management with developer self-service capability}{Ensures security compliance while maintaining developer productivity}
      \aexpbullet {Integrated vulnerability detection into dev cycles}{Accelerated CVE resolution via developer self-service}
      \aexpbullet {Integrated Sonar, AWS Inspector, and dependency checks.}{Ensuring 0 critical/high CVEs in production}
      \aexpbullet {Built automatic resolution of AWS Security Hub alerts tailored to our workload}{Maintained >90\% compliance score for audits}
    }

    \expmultibullet {FinOps and engagement}{Spearheaded FinOps adoption across engineering teams}
    {
      \aexpbullet {Drive Cloud optimization with deep collaboration with engineering leadership team.}{Reduced AWS cost by 50k\$ per month}
      \aexpbullet {Standardized JVM parameters and CPU memory configs}{Improved throughput and EKS cluster compaction by 20\%}
      \aexpbullet {Implemented tagging, cost dashboards, and usage policies}{Improved cost visibility and accountability across 20 accounts.}
      \aexpbullet {Mentored teams on AWS cost efficiency and tagging best practices.}{drove cultural shift toward shared FinOps ownership}
      \item       {Regular cost reviews with Finance team to Understand OpEx expectations from business and align the resources accordingly.}
      \aexpbullet {Collaborated with AWS TAM and architects.}{Proactively mitigated potential infrastructure, security and cost issues}
      \item {Collaborated with Google for AI related engagements and DR cloud setup.}
    }

    \expbullet {COVID Response}{As part of WFH movement of entire company of \textasciitilde 1000 employees, Defined and led the secure user authentication process
      using Akamai Zero Trust and two-way SSL handshake (Hashicorp Vault), securely authenticating the employee to internal network }
    {Business continuity with zero security lapses.}

    \expmultibullet {Data center to AWS migration}
    {Designed and drove the cloud migration strategy for core services to an AWS, working closely with engineering,
      network and security teams. Focused on defining architecture standards,
      deployment patterns, and phased service cutover plans with active data center sync.}{
      \item Uptime improved to beyond 99.9\% including planned downtimes which led to fewer business impacts.
      \item Reduced cluster rebuild time to less than 1 hour for catastrophic failures ensuring quick disaster recovery for continued operations.
      \item Improved latency by over 50\% Increased organic traffic and SEO ranking.
    }
  \end{experiencebullets}

\end{experience}

\begin{experience}{Principal Software Engineer}{Digilend.in}{2017-2019, Bangalore}
  {\textbf{[FinTech lending platform]} Part of the \textbf{early startup team},
    working directly with the founders. Delivered features across the stack and also maintaining the \textbf{AWS Cloud (EC2, RDS)}
  }
  \begin{experiencebullets}
    \expbullet {Behavior model}{Built real-time user behavior tracking and dynamic journeys based on behavior}{Improved user loan approval rates by 15\%.}
    \expbullet {Website Performance}{Refactored and reduced AngularJS bundle size for key customer flows}{Reduce page load time to under 15(sec) and improved experience for customers with unreliable internet}
    \expbullet {Business Operations Automation}{Automated filling of loan application forms to reduce errors and improve on-ground agent performance.}{Document collection time reduced to less than 15 minutes per customer.}
  \end{experiencebullets}
\end{experience}


\begin{experience}{Software Specialist}{Hewlett Packard Enterprise}{2011-2017, Bangalore}{Worked on enterprise tape storage management tool, focusing on UI modernization, API design, and cross-release feature development.}
  \begin{experiencebullets}
    \item \textbf{[UI Modernization]} Designed new UI according to HPE UI guidelines and Lead the team of 4 engineers to implement them as a transition from Flash to HTML5/React.js.
    \item \textbf{[Rest API design]} Defined and delivered RESTful APIs for new React UI.
  \end{experiencebullets}
\end{experience}

\begin{experience}{Software Engineer}{IBM India Software Labs}{2008-2011, Bangalore}{Full-stack engineer and lab systems administrator working on management tool for IBM Power Systems.}
  \begin{experiencebullets}
    \item \textbf{[Full-Stack Development]} Delivered UI/backend features, bug fixes across multiple releases of the Power Management Console.
    \item \textbf{[Data center management]} Planned, Implemented and Maintained lab test environments for continuous development using DS5000, N3600, VMware ESXi and IBM power servers.
  \end{experiencebullets}
\end{experience}

\section*{Awards \& Recognition}
\begin{itemize}[leftmargin=*, itemsep=0em]
  \item First place in Circuit Design during Eccentric 2006, Dept. of E\&C, MSRIT, Bangalore.
  \item Top 10 team in “Mission to Mars”, Shasthra 2007, IIT Madras.
\end{itemize}


\section*{Education, Certifications \& Online Learning}

\textbf{Bachelor of Engineering in Electronics \& Communication} \\
Sapthagiri College of Engineering (VTU), Bangalore \hfill \textit{Aggregate: 75.90\%} \textit{2004–2008}  \\

\vspace{0.5em}
\textbf{Cryptography - I, Prof. Dan Boneh, Stanford University - Coursera} \hfill \textit{Sep 2013} \\

\textbf{Machine Learning, Prof. Andrew Ng, Stanford University - Coursera} \hfill \textit{Dec 2011} \\

\end{document}
