\documentclass[11pt]{article}
\usepackage[a4paper,margin=0.75in]{geometry}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{multicol}
\definecolor{myblue}{RGB}{27,133,184}
\colorlet{bodytext}{black!80}  % or black!85 for slightly darker
\linespread{1.1}
\usepackage{fontspec}
\setmainfont{TeX Gyre Heros} % beautiful, full character set
\setsansfont{TeX Gyre Heros}   % matches well

\titleformat{\section}
  [block]
  {\Large\sffamily}{}{0pt}{\color{black}}[\color{myblue}\vspace{0.3ex}\hrule height 3pt width 1\textwidth]

% === Reusable Experience Block Header ===
\newcommand{\roleheader}[3]{%
  {\large\sffamily\textbf{#1} @ #2} \hfill \textit{#3}\\[-0.3em]
  \color{myblue}\rule{\linewidth}{1pt}\\[0.5em]\color{bodytext}
}

% === Experience Bullets Environment ===
\newenvironment{experiencebullets}{%
  \begin{itemize}[leftmargin=1.25em, itemsep=-0.25em]
    \renewcommand{\labelitemi}{\textbullet}
}{%
  \end{itemize}
}

\newenvironment{experience}[4]{%
  \roleheader{#1}{#2}{#3}%
  #4\vspace{0.5em}%
}{%
  \vspace{1em}
}

% === Experience Bullet Point with Action → Impact ===
\newcommand{\expbullet}[3]{%
  \item \textbf{[#1]} {#2} \textrightarrow{} \textit{#3}%
}

\newcommand{\aexpbullet}[2]{%
  \item {#1} \textrightarrow{} \textit{#2}%
}

\newcommand{\expsubsection}[1]{%
  \vspace{0.75em}%
  {\sffamily\bfseries #1}\\[-0.2em]
  \rule{0.15\linewidth}{1pt}\\[0.3em]
}

\newenvironment{impactsection}[2]{%
  \vspace{0.5em}%
  \textbf{[#1]}\\#2%
  \begin{itemize}[leftmargin=2em, itemsep=-1em]
}{%
  \end{itemize}
}

\newlist{arrowitem}{itemize}{1}
\setlist[arrowitem]{label=\textrightarrow{}, leftmargin=2em, noitemsep, topsep=0pt}

\newcommand{\expmultibullet}[3]{%
  \item \textbf{[#1]} #2
  \begin{arrowitem}
    #3
  \end{arrowitem}
}

\newcommand{\name}[1]{\noindent{\LARGE\sffamily\textbf{#1}}}
\newcommand{\contact}[1]{\begin{flushright} \small #1 \end{flushright}}
\usepackage[none]{hyphenat}
\raggedright

\begin{document}
\pagestyle{empty}
\color{bodytext}

\name{Srinath H S}\\[0.5em]
\textbf{Technology Leader | Scaling Platforms, People, and Strategy for High-Growth Businesses}\\[0.3em]
srinath.hs@gmail.com \quad | \quad +91 95387 88470 \quad | \quad linkedin.com/in/srinathhs

17+ years building scalable, secure platforms (1M+ DAUs) and managing high-performing engineering teams. Experienced in defining technical vision, mentoring and growing talent, and aligning platform strategy with business goals.

\section*{Core Competencies}
\begin{itemize}[leftmargin=*, itemsep=-0.5em]
  \item \textbf{Leadership \& People Management:} Built, scaled, and mentored engineering teams of 20+, fostering ownership, accountability, and career growth.
  \item \textbf{Strategic Technology Direction:} Partnering with executives to shape long-term architecture, cloud strategy, and security posture aligned with business goals.
  \item \textbf{Program \& Delivery Management:} Driving initiatives from conception to delivery through structured planning, stakeholder alignment, and cross-functional execution.
  \item \textbf{Cloud Architecture \& DevOps:} AWS, Kubernetes, Terraform, Ansible, microservices.
  \item \textbf{DevSecOps \& Governance:} Embedding security into development, compliance readiness (ISO, PCI), automated incident response.
  \item \textbf{FinOps \& Cost Optimization:} Cloud cost reduction, resource efficiency, financial accountability.
\end{itemize}

\section*{Experience}

\begin{experience}{Principal Architect}{Bankbazaar.com}{2019-Present, Bangalore}{%
    Leading the \textbf{Cloud Platform, DevOps, and Security strategy} for a product ecosystem \textbf{serving 1M+ DAUs}. Driving organizational transformation across scalability, developer productivity, security, and cost governance. Reporting into CTO and working with C-suite on long-term platform vision.%
  }

  \begin{experiencebullets}
    \item \textbf{[Leadership \& Talent Development]} Scaled and mentored a 20+ member platform engineering team, establishing growth paths, instituting performance reviews, and sponsoring engineers for leadership roles.

    \item \textbf{[Executive Collaboration]} Partnered with Product, Business, and Operations leadership to align platform evolution with business strategy, ensuring technology investments directly supported growth and compliance goals.

    \expbullet{Engineering Culture}{Defined org-wide standards in microservices, observability, and CI/CD}{20+ development teams improved delivery velocity and resilience, establishing a culture of engineering excellence.}

    \expbullet{Platform Strategy}{Institutionalized Infrastructure as Code and self-service DevOps platforms}{Reduced new service onboarding to <1hr, shifted responsibility to product teams, and improved developer ownership.}

    \expbullet{Compliance \& Certifications}{Led PCI DSS and ISO 27001 certification initiatives for engineering}{Successfully passed external audits with no major findings, ensuring continued ability to partner with banks and financial institutions.}

    \expbullet{Regulatory Representation}{Represented platform engineering during bank and regulator audits}{Built trust with external stakeholders by demonstrating technical controls, security posture, and compliance readiness.}

    \expbullet{AI Adoption}{Directed company-wide AI strategy and secured leadership buy-in}{Accelerated developer productivity via copilots, initiated BI automation, and launched AI-driven customer experience initiatives.}

    \expbullet{Security Leadership}{Embedded security into developer workflows via automated vulnerability management}{Maintained >90\% compliance with zero critical CVEs in production, while reducing developer friction.}

    \expbullet{FinOps Governance}{Established cost visibility and accountability across 20+ AWS accounts}{Cut AWS spend by \$50k/month and improved financial predictability for leadership.}

    \expbullet{Crisis Leadership}{Directed secure remote access program during COVID}{Enabled 1000+ employees to work remotely with zero security lapses.}

    \expbullet{Strategic Transformation}{Led migration from on-prem data center to AWS}{Achieved >99.9\% uptime, reduced DR recovery to <1hr, and boosted SEO ranking through latency improvements.}
  \end{experiencebullets}

\end{experience}

\begin{experience}{Principal Software Engineer}{Digilend.in}{2017-2019, Bangalore}{%
  Member of the early startup team, working directly with founders to define the technology roadmap and delivery priorities. \textbf{Led end-to-end platform engineering}, combining hands-on contribution with mentoring of junior developers and ownership of cloud infrastructure.%
}
  \begin{experiencebullets}
    \item \textbf{[Leadership in Startup Environment]} Established engineering practices, guided product roadmap execution, and mentored the first set of developers in architecture, coding, and delivery discipline.

    \expbullet{Product Evolution}{Directed design and delivery of real-time behavior tracking and adaptive loan journeys}{Improved loan approval rates by 15\%, directly impacting revenue.}

    \expbullet{Customer Experience}{Oversaw UI optimization and performance initiatives across AngularJS stack}{Reduced key customer flow load times to under 15s, improving experience for users with poor connectivity.}

    \expbullet{Operational Efficiency}{Automated critical agent workflows including loan application handling}{Cut document collection time to <15 minutes per customer, improving operational throughput.}

    \expbullet{Cloud Ownership}{Owned AWS infrastructure (EC2, RDS), ensuring secure, scalable deployments}{Enabled rapid product iteration without outages, supporting business growth.}
  \end{experiencebullets}
\end{experience}

\begin{experience}{Software Specialist}{Hewlett Packard Enterprise}{2011-2017, Bangalore}{%
  Worked on enterprise tape storage management tools, contributing to UI modernization, API design, and cross-release feature development. Played a coordinating role across design and development teams.%
}
\end{experience}

\begin{experience}{Software Engineer}{IBM India Software Labs}{2008-2011, Bangalore}{%
  Full-stack engineer and lab systems administrator, delivering features for IBM Power Systems management tools and maintaining test environments across data centers.%
}
\end{experience}

\section*{Education, Certifications \& Online Learning}

\textbf{Bachelor of Engineering in Electronics \& Communication} \\
Sapthagiri College of Engineering (VTU), Bangalore \hfill \textit{Aggregate: 75.90\%} \textit{2004–2008}  \\

\vspace{0.5em}
\textbf{Cryptography - I, Prof. Dan Boneh, Stanford University - Coursera} \hfill \textit{Sep 2013} \\

\textbf{Machine Learning, Prof. Andrew Ng, Stanford University - Coursera} \hfill \textit{Dec 2011} \\

\end{document}
